---
title: "Carat to Price Relationship in Diamonds using Shiny"
author: "Jagannatha Reddy"
date: "12/26/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
- application is build to demonstrate few features of Shiny
- hosted at R Studio Shiny Sever. Click <a href="https://jaganrn.shinyapps.io/DataScience-DevelopingDataProducts-ShinyProject/">this link</a> to access 
- **diamonds** data from in ggplot2 is used for analysis. Sample data given below

```{r echo=TRUE, fig.align='center', results=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)
head(diamonds,4)
```

## Analysis by Diamond Cuts
- cut: significantly affects appearance and value
- one of the four Cs of diamond grading, the others being carat, color, and clarity
- The following table shows number of records for each Cut
```{r echo=TRUE, fig.align='center', results=FALSE, warning=FALSE, message=FALSE, comment="#"}
table(diamonds$cut)
```
- select one or more Cuts for which analysis to be done
- also chose the sample size and line size for plotting the data
- Price by Carat shown for selected Cuts by each Clarity

## Analysis by Diamond Clarity
- clarity: relates to existence and visual appearance of internal characteristics
- one of the four Cs of diamond grading, the others being carat, color, and cut
- The following table shows number of records for each Clarity
```{r echo=TRUE, fig.align='center', results=FALSE, warning=FALSE, message=FALSE, comment="#"}
table(diamonds$clarity)
```
- select one or more Clarities for which analysis to be done
- also chose the sample size and line size for plotting the data
- Price by Carat shown for selected Clarities by each Cut

## Summary
- sample from **diamonds** data from in ggplot2 used for analysis
- application demonstrates few features of Shiny. The features exposed are: Tab, CheckBox, Numeric Input, Action Buttion, Observer, Several Output functions
- Legend information is sourced from the following websites:
    a. http://www.lumeradiamonds.com/diamond-education/diamond-cut
    b. http://4cs.gia.edu/en-us/diamond-clarity/
- Application hosted at <a href="https://jaganrn.shinyapps.io/DataScience-DevelopingDataProducts-ShinyProject/">this link</a> 
